AI-Based Detection of Jamming Attacks In 6G Drone Networks

### 2024-09-13 article.tex
Continued introduction

>>>>

AI integration in 6G networks will greatly strengthen the security of the network against security threats. 
By leveraging Diagnostic Analytics, a collection of insights into the status of the networks, security teams 
will be able to train specific AI models to detect and respond to security threats in real-time.

In this paper we will focus on a specific aspect of the security of 6G networks, namely the detection of 
jamming attacks in drone networks.
